Utilizing Parallel Workers: LLVM's Vectorization Plan

### 2025-01-27 paper/paper.tex
paper

\section{Summary and Future Work}
\label{sec:summary}
In conclusion, VPlan has been in active development for several years now. When compiling with LLVM, 
VPlans are used to model different vectorization approaches. They do so by adding a new layer of 
abstraction over the underlying LLVM IR. This VPlan layer uses \texttt{VPRecipes} to model 
vectorization-specific instructions. 
This abstraction allows for efficiently exploring many optimization decisions simultaneously, 
keeping the underlying implementation flexible and modular. In the end, a cost model currently 
working based on LLVM IR instead of \texttt{VPRecipes} is used to compare different VPlans 
and choose the most optimal one. Finally, this chosen VPlan is executed, materializing its \texttt{VPRecipes} 
back into LLVM IR.

@@

% TODO: Write about potential future work benchmarking
%       Loop Code Benchmark collection
%       Quick note about collaborative development (example stability & miscompile policy)
%       LLVM Loop Optimization as one of the most active subareas of LLVM development
% TODO: "Also, it would be great to have the main problem and paper’s aim to be re-stated in the summary section for the first reading pass."
%       "summary lacks the problem statement and the big picture"

>>>>

\section{Summary and Future Work}
\label{sec:summary}
Compilers have been using auto-vectorization to help developers optimize their code 
across platforms by making the best possible use of a target's SIMD capabilities. Over the years, 
LLVM's original auto-vectorization system evolved into an inflexible pipeline, making it hard 
to adapt to new features like outer-loop vectorization.

As a solution, Intel proposed a new modular system called VPlan.
By now, VPlan has been in active development for several years. 
This system would use different VPlan objects to efficiently 
model and explore different vectorization approaches simultaneously.
It adds a new layer using \texttt{VPRecipes} to model 
vectorization-specific instructions over the underlying LLVM IR. 
This abstraction allows for efficiently exploring different optimization decisions simultaneously, 
keeping the underlying implementation flexible and modular. In the end, a cost model currently still 
working based on LLVM IR instead of \texttt{VPRecipes} is used to compare different VPlans 
and choose the most optimal one. Finally, this chosen VPlan is executed, materializing its \texttt{VPRecipes} 
back into LLVM IR.

@@

% TODO: Write about potential future work benchmarking
%       Loop Code Benchmark collection
%       Quick note about collaborative development (example stability & miscompile policy)
%       LLVM Loop Optimization as one of the most active subareas of LLVM development
